Output Summary

### 2022-01-05 03-post-process/compare-sim-to-obs.Rmd
Change name of f to E throughout (deals with eggs)

```{r}
x = lapply(1:4, function(j) get_ratio("^Pb_per_f_tot[year,pop]", obs_y, sim_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Egg to Parr Survival: Estimates")
ratio_plots(x, "Egg to Parr Survival: Ratios")
est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "FW Juvenile", Type = "Egg to Parr Survival"))
```

@@

```{r}
x = lapply(1:4, function(j) get_ratio("^f_tot[year,pop]", obs_y, sim_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Total Egg Production: Estimates")
ratio_plots(x, "Total Egg Production: Ratios")
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Abundance", Type = "Total Egg Production"))
```

@@

```{r}
pop_ts_plots("^Pb_per_f_tot[year,pop]")
```

@@

```{r}
pop_ts_plots("^f_tot[year,pop]")
```

>>>>

```{r}
x = lapply(1:4, function(j) get_ratio("^Pb_per_E[year,pop]", obs_y, sim_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Egg to Parr Survival: Estimates")
ratio_plots(x, "Egg to Parr Survival: Ratios")
est_ratios = rbind(est_ratios, summarize_ratios(x, Class = "FW Juvenile", Type = "Egg to Parr Survival"))
```

@@

```{r}
x = lapply(1:4, function(j) get_ratio("^E[year,pop]", obs_y, sim_y, pop = j))
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Total Egg Production: Estimates")
ratio_plots(x, "Total Egg Production: Ratios")
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Abundance", Type = "Total Egg Production"))
```

@@

```{r}
pop_ts_plots("^Pb_per_E[year,pop]")
```

@@

```{r}
pop_ts_plots("^E[year,pop]")
```

### 2022-01-05 03-post-process/output-plots.Rmd
Change name of f to E throughout (deals with eggs)

---
title: "Output Summary"
subtitle: "Multi-Population Model"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "base"
    input: text
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
    input: checkbox
editor_options: 
  chunk_output_type: console
---

@@

```{r calculate-mcmc-diagnostics}
# parr recruitment
L1 = "Parr Recruitment"
L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "Process SD", "Among-pop Correlation", "Parr States")
match = c("alpha", "^beta[", "mu_beta_per_wul", "sig_lbeta", "sig_lPb", "rho_lPb", "^Pb[")
parr_recruit_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

@@

  out = list(
    egg_to_parr_surv = post_summ(post, sub_index("^lPb_resid[.+,pop]", pop = j))["mean",],
    p_fall_mig = post_summ(post, sub_index("^Lpi_resid[.+,pop]", pop = j))["mean",],
    ow_surv_fall = post_summ(post, sub_index("^Lphi_Pa_Mb_resid[.+,LH_type,pop]", pop = j, LH_type = 1))["mean",],
    ow_surv_spring = post_summ(post, sub_index("^Lphi_Pa_Mb_resid[.+,LH_type,pop]", pop = j, LH_type = 2))["mean",],
    toLGR_surv_nor = post_summ(post, sub_index("^Lphi_Mb_Ma_resid[.+,origin,pop]", pop = j, LH_type = 2, origin = 1))["mean",],
    toLGR_surv_hor = post_summ(post, sub_index("^Lphi_Mb_Ma_resid[.+,origin,pop]", pop = j, LH_type = 2, origin = 2))["mean",],
    LGR_to_BON_surv_nor = post_summ(post, sub_index("^Lphi_Ma_O0_resid[.+,origin]", origin = 1))["mean",],
    LGR_to_BON_surv_hor = post_summ(post, sub_index("^Lphi_Ma_O0_resid[.+,origin]", origin = 2))["mean",],
    yr1_ocean_surv = post_summ(post, sub_index("^Lphi_O0_O1_resid[.+,1,pop]", pop = j))["mean",-1],
    age3_mat_nor = post_summ(post, sub_index("^Lpsi_O1_Rb_resid[.+,origin,pop]", origin = 1, pop = j))["mean",],
    age3_mat_hor = post_summ(post, sub_index("^Lpsi_O1_Rb_resid[.+,origin,pop]", origin = 2, pop = j))["mean",],
    age4_mat_nor = post_summ(post, sub_index("^Lpsi_O2_Rb_resid[.+,origin,pop]", origin = 1, pop = j))["mean",],
    age4_mat_hor = post_summ(post, sub_index("^Lpsi_O2_Rb_resid[.+,origin,pop]", origin = 2, pop = j))["mean",],
    BON_to_LGR_surv_nor = post_summ(post, sub_index("^Lphi_Rb_Ra_resid[.+,origin]", origin = 1))["mean",],
    BON_to_LGR_surv_hor = post_summ(post, sub_index("^Lphi_Rb_Ra_resid[.+,origin]", origin = 2))["mean",],
    prespawn_surv = post_summ(post, sub_index("Lphi_Sb_Sa_resid[.+,pop]", pop = j))["mean",]
  )
  out = do.call(cbind, out)
  rownames(out) = NULL
  out
}
```

@@

  # extract posterior summaries of total egg production by brood year
  f_tot = post_summ(post, sub_index("^f_tot[year,pop]", pop = j, year = ts_yrs))

@@

  # predict parr recruits along a sequence of spawner abundances
  Sa_pred = seq(0, max(Sa_tot[5,]), length = 30)
  f_pred = seq(0, max(f_tot[5,]), length = 30)

  Pb_pred = t(sapply(1:post_dim(post, "saved"), function(i) BH(f_pred, bh_params[i,1], bh_params[i,2])))
  colnames(Pb_pred) = paste0("Pb_pred[", 1:length(Sa_pred), "]")
  Pb_pred = post_convert(cbind(postpack:::id_mat(post), Pb_pred))
  Pb_pred = post_summ(Pb_pred, "Pb_pred")

@@

  # empty plot
  plot(1, 1, type = "n", xlim = range(0, f_tot[5,]), ylim = range(0, Pb[5,], Pb_pred[5,]),
       xlab = "", ylab = "", xaxt = "n", yaxt = "n", main = pops[j])

@@

  # draw fitted relationship: Bayesian
  polygon(c(f_pred, rev(f_pred)), c(Pb_pred[4,], rev(Pb_pred[5,])), col = alpha("salmon", 0.5), border = NA)
  lines(Pb_pred[4,] ~ f_pred, col = "red", lty = 2)
  lines(Pb_pred[5,] ~ f_pred, col = "red", lty = 2)
  lines(Pb_pred[3,] ~ f_pred, col = "red", lwd = 2)

  # draw state pairs + uncertainty
  segments(f_tot[4,], Pb[3,], f_tot[5,], Pb[3,], col = alpha("red", 0.5))
  segments(f_tot[3,], Pb[4,], f_tot[3,], Pb[5,], col = alpha("red", 0.5))
  points(Pb[3,] ~ f_tot[3,], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
}

@@

  # empty plot
  plot(f_tot["mean",] ~ Sa_tot["mean",],
       ylim = c(0, max(f_tot["97.5%",])),
       xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
       ylab = "", xlab = "", las = 1, yaxt = "n")

@@

  segments(Sa_tot["2.5%",], f_tot["mean",], Sa_tot["97.5%",], f_tot["mean",], col = alpha("red", 0.5))
  segments(Sa_tot["mean",], f_tot["2.5%",], Sa_tot["mean",], f_tot["97.5%",], col = alpha("red", 0.5))
  points(f_tot["mean",] ~ Sa_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
  abline(c(0, 1000), lty = 1)
  abline(c(0, 1800), lty = 2)
  abline(c(0, 3600), lty = 3)

@@

```{r parr-per-egg-v-eggs, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  # extract posterior summaries of total egg production by brood year
  f_tot = post_summ(post, sub_index("^f_tot[year,pop]", pop = j, year = ts_yrs))

  # conversion rates
  Pb_per_f_tot = post_summ(post, sub_index("^Pb_per_f_tot[year,pop]", pop = j, year = ts_yrs))

@@

  # empty plot
  plot(Pb_per_f_tot["mean",] ~ f_tot["mean",],
       # ylim = c(0, max(Pb_per_f_tot["97.5%",], alpha["97.5%",])),
       ylim = c(0, 1),
       xlim = c(0, max(f_tot["97.5%",])), type = "n",
       ylab = "", xlab = "", las = 1, xaxt = "n", main = pops[j])

@@

  segments(f_tot["2.5%",], Pb_per_f_tot["mean",], f_tot["97.5%",], Pb_per_f_tot["mean",], col = alpha("red", 0.5))
  segments(f_tot["mean",], Pb_per_f_tot["2.5%",], f_tot["mean",], Pb_per_f_tot["97.5%",], col = alpha("red", 0.5))
  points(Pb_per_f_tot["mean",] ~ f_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)

@@

```{r recruit-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,4))
my_boxplot("^alpha[.]$", "Productivity")
my_boxplot("^beta[.]$", "Capacity")
my_boxplot("^sig_lPb[.]$", "Process SD")
my_boxplot("^rho_lPb", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)
```

>>>>

---
title: "Output Summary"
subtitle: "Multi-Population Model"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "new-BH"
    input: text
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
    input: checkbox
editor_options: 
  chunk_output_type: console
---

@@

```{r calculate-mcmc-diagnostics}
# parr recruitment
L1 = "Egg-to-Parr Survival"
L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "Process SD", "Among-pop Correlation", "Realized Survival", "Parr States")
match = c("alpha", "^beta[", "mu_beta_per_wul", "sig_lbeta", "sig_Lphi_E_Pb", "rho_Lphi_E_Pb", "^phi_E_Pb[", "^Pb[")
parr_recruit_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

@@

  out = list(
    egg_to_parr_surv = post_summ(post, sub_index("^Lphi_E_Pb_resid[.+,pop]", pop = j))["mean",],
    p_fall_mig = post_summ(post, sub_index("^Lpi_resid[.+,pop]", pop = j))["mean",],
    ow_surv_fall = post_summ(post, sub_index("^Lphi_Pa_Mb_resid[.+,LH_type,pop]", pop = j, LH_type = 1))["mean",],
    ow_surv_spring = post_summ(post, sub_index("^Lphi_Pa_Mb_resid[.+,LH_type,pop]", pop = j, LH_type = 2))["mean",],
    toLGR_surv_nor = post_summ(post, sub_index("^Lphi_Mb_Ma_resid[.+,origin,pop]", pop = j, LH_type = 2, origin = 1))["mean",],
    toLGR_surv_hor = post_summ(post, sub_index("^Lphi_Mb_Ma_resid[.+,origin,pop]", pop = j, LH_type = 2, origin = 2))["mean",],
    LGR_to_BON_surv_nor = post_summ(post, sub_index("^Lphi_Ma_O0_resid[.+,origin]", origin = 1))["mean",],
    LGR_to_BON_surv_hor = post_summ(post, sub_index("^Lphi_Ma_O0_resid[.+,origin]", origin = 2))["mean",],
    yr1_ocean_surv = post_summ(post, sub_index("^Lphi_O0_O1_resid[.+,1,pop]", pop = j))["mean",-1],
    age3_mat_nor = post_summ(post, sub_index("^Lpsi_O1_Rb_resid[.+,origin,pop]", origin = 1, pop = j))["mean",],
    age3_mat_hor = post_summ(post, sub_index("^Lpsi_O1_Rb_resid[.+,origin,pop]", origin = 2, pop = j))["mean",],
    age4_mat_nor = post_summ(post, sub_index("^Lpsi_O2_Rb_resid[.+,origin,pop]", origin = 1, pop = j))["mean",],
    age4_mat_hor = post_summ(post, sub_index("^Lpsi_O2_Rb_resid[.+,origin,pop]", origin = 2, pop = j))["mean",],
    BON_to_LGR_surv_nor = post_summ(post, sub_index("^Lphi_Rb_Ra_resid[.+,origin]", origin = 1))["mean",],
    BON_to_LGR_surv_hor = post_summ(post, sub_index("^Lphi_Rb_Ra_resid[.+,origin]", origin = 2))["mean",],
    prespawn_surv = post_summ(post, sub_index("Lphi_Sb_Sa_resid[.+,pop]", pop = j))["mean",]
  )
  out = do.call(cbind, out)
  rownames(out) = NULL
  out
}
```

@@

  # extract posterior summaries of total egg production by brood year
  E = post_summ(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs))

@@

  # predict parr recruits along a sequence of spawner abundances
  Sa_pred = seq(0, max(Sa_tot[5,]), length = 30)
  E_pred = seq(0, max(E[5,]), length = 30)

  Pb_pred = t(sapply(1:post_dim(post, "saved"), function(i) BH(E_pred, bh_params[i,1], bh_params[i,2])))
  colnames(Pb_pred) = paste0("Pb_pred[", 1:length(Sa_pred), "]")
  Pb_pred = post_convert(cbind(postpack:::id_mat(post), Pb_pred))
  Pb_pred = post_summ(Pb_pred, "Pb_pred")

@@

  # empty plot
  plot(1, 1, type = "n", xlim = range(0, E[5,]), ylim = range(0, Pb[5,], Pb_pred[5,]),
       xlab = "", ylab = "", xaxt = "n", yaxt = "n", main = pops[j])

@@

  # draw fitted relationship: Bayesian
  polygon(c(E_pred, rev(E_pred)), c(Pb_pred[4,], rev(Pb_pred[5,])), col = alpha("salmon", 0.5), border = NA)
  lines(Pb_pred[4,] ~ E_pred, col = "red", lty = 2)
  lines(Pb_pred[5,] ~ E_pred, col = "red", lty = 2)
  lines(Pb_pred[3,] ~ E_pred, col = "red", lwd = 2)

  # draw state pairs + uncertainty
  segments(E[4,], Pb[3,], E[5,], Pb[3,], col = alpha("red", 0.5))
  segments(E[3,], Pb[4,], E[3,], Pb[5,], col = alpha("red", 0.5))
  points(Pb[3,] ~ E[3,], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
}

@@

  # empty plot
  plot(E["mean",] ~ Sa_tot["mean",],
       ylim = c(0, max(E["97.5%",])),
       xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
       ylab = "", xlab = "", las = 1, yaxt = "n")

@@

  segments(Sa_tot["2.5%",], E["mean",], Sa_tot["97.5%",], E["mean",], col = alpha("red", 0.5))
  segments(Sa_tot["mean",], E["2.5%",], Sa_tot["mean",], E["97.5%",], col = alpha("red", 0.5))
  points(E["mean",] ~ Sa_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
  abline(c(0, 1000), lty = 1)
  abline(c(0, 1800), lty = 2)
  abline(c(0, 3600), lty = 3)

@@

```{r parr-per-egg-v-eggs, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  # extract posterior summaries of total egg production by brood year
  E = post_summ(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs))

  # conversion rates
  Pb_per_E = post_summ(post, sub_index("^Pb_per_E[year,pop]", pop = j, year = ts_yrs))

@@

  # empty plot
  plot(Pb_per_E["mean",] ~ E["mean",],
       ylim = c(0, 1),
       xlim = c(0, max(E["97.5%",])), type = "n",
       ylab = "", xlab = "", las = 1, xaxt = "n", main = pops[j])

@@

  segments(E["2.5%",], Pb_per_E["mean",], E["97.5%",], Pb_per_E["mean",], col = alpha("red", 0.5))
  segments(E["mean",], Pb_per_E["2.5%",], E["mean",], Pb_per_E["97.5%",], col = alpha("red", 0.5))
  points(Pb_per_E["mean",] ~ E["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)

@@

```{r recruit-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,4))
my_boxplot("^alpha[.]$", "Productivity")
my_boxplot("^beta[.]$", "Capacity")
my_boxplot("^sig_Lphi_E_Pb[.]$", "Process SD")
my_boxplot("^rho_Lphi_E_Pb", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)
```
